{\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment

### 2020-08-18 documents/supplemental.tex
IT.IS models
Extract distribution

>>>>

\PRLsep{{\itshape Sampling time-domain spectrometry}}

\begin{quote}
A rapidly increasing voltage step V tŽ . is applied to the 0
line and recorded, along with the reflected voltage R tŽ .
returned from the sample and delayed by the cable propagation time Figure 2 . Any cable or instrument artifacts Ž .
are separated from the sample response due to the propagation delay, thus making them easy to identify and control. The entire frequency spectrum is captured at once,
thus eliminating drift and distortion between frequencies.
\end{quote}

The pulse is usually recorded in real-time with a many-GHz oscilloscope. However, by using a sampling oscilloscope, massively undersampling the signal,

Another advantage of this technique is that no high-Q filters are required to select the frequency;
discrimination is in the time-domain, and is spread out over many seconds. It is also much easier to generate a 10+ GHz fast edge than it is to generate a CW signal.
